Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-11-19 paper/results.tex
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@670 3fc257bb-8550-0410-81b3-a5c103da83f7
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@671 3fc257bb-8550-0410-81b3-a5c103da83f7

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
Algorithm & R-MAT & R-MAT & PageRank & Tri & CC & MIS & SSSP & SSSP \\
\hline
Line count & 208 & 216 & 694 & 367 & 453 & 393 & 505 & 569 \\
Figure & \ref{fig:rmat} & \ref{fig:rmat2} & \ref{fig:pr2} & \ref{fig:tri} & \ref{fig:cc} & \ref{fig:luby} & \ref{fig:sssp} & \ref{fig:sssp2} \\
\hline
\end{tabular}
\caption{Line counts of codes that implement each of the graph
  algorithms in the associated figures.}
\label{t:rmat}
\end{center}
\end{table}

For comparison, we wrote a parallel distributed-memory R-MAT
generation code with explicit MPI calls using a different
(non-MapReduce) algorithm than that of Figures \ref{fig:rmat} and
\ref{fig:rmat2}.  It required 1842 lines of code, mainly because it
must implement the parallelism explicitly whereas the codes of this
section relegate that task to the MR-MPI library.  Our collaborators
(see Acknowledgements) have a Hadoop implementation of the SSSP
algorithm of Figure \ref{fig:sssp}.  It required XXX lines of Java
code.

>>>>

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
Algorithm & R-MAT & R-MAT++ & PageRank & Tri & CC & MIS & SSSP & SSSP++ \\
\hline
Lines of code & 208 & 216 & 694 & 367 & 453 & 393 & 505 & 569 \\
Figure & \ref{fig:rmat} & \ref{fig:rmat2} & \ref{fig:pr2} & \ref{fig:tri} & \ref{fig:cc} & \ref{fig:luby} & \ref{fig:sssp} & \ref{fig:sssp2} \\
\hline
\end{tabular}
\caption{Lines of code to implement each of the graph
  algorithms in the associated figures.}
\label{t:rmat}
\end{center}
\end{table}

For comparison, we wrote a parallel distributed-memory R-MAT
generation code with explicit MPI calls using a different
(non-MapReduce) algorithm than that of Figures \ref{fig:rmat} and
\ref{fig:rmat2}.  It required 1006 lines of code, mainly because it
must implement the parallelism explicitly whereas the codes of this
section relegate that task to the MR-MPI library.  A similar all-MPI
implementation of the PageRank algorithm required 1206 lines.  By
contrast an implementation of PageRank using the Trilinos parallel
linear algebra library (discussed in Section
\ref{subsec:results_pagerank}) required only 153 lines of code, since
an entire matrix-vector multiply can be invoked by a single call to
Trilinos.  Our collaborators (see Acknowledgements) have a Hadoop
implementation of the SSSP algorithm of Figure \ref{fig:sssp}.  It
required XXX lines of Java code.
